---
title: "Opioid EWSS - Weekly Data Summary"
category: "Confidential"
author: "Peterborough Public Health"
date: "`r Sys.Date()`"
output: 
  officedown::rdocx_document:
    reference_docx: I:/Opioids/Data Analyses/styles/Template - PPH reports - R markdown.docx
    fig_width: 7
    fig_height: 3
    page_size:
      width: 8.5
      height: 11
    page_margins:
      gutter: 0
    

---
<!--- NOTE: R setup --->

```{r global-setup}
#| echo = FALSE,
#| include = FALSE,
#| cache = FALSE

# SETUP: R MARKDOWN ----
#-----------------------------------------------------------------------------#
# LOAD PACKAGES ----
#-----------------------------------------------------------------------------#
knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)
library(officedown)
library(officer)
library(rvg)
library(flextable)
fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

#-----------------------------------------------------------------------------#
# SPECIFY OUTPUT FORMATTING ----
#-----------------------------------------------------------------------------#
EMS_colour = "#29846b"
ED_colour = "#57AACB"
EWSS_colour = "#d60093"

# > Summary Tables Formatting ----
EMS_border = officer::fp_border(color = EMS_colour, width = 1)
ED_border = officer::fp_border(color = ED_colour, width = 1)
EWSS_border = officer::fp_border(color = EWSS_colour, width = 1)

# SETUP: ANALYSES ----
#-----------------------------------------------------------------------------#
# LOAD PACKAGES ----
#-----------------------------------------------------------------------------#
library(readr)
library(plyr)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(rlang)
library(tidyverse)
library(grid)
library(janitor)
library(scales)

#------------------------------------------------------------------------------#
# BACKGROUND: DATASETS ----
#------------------------------------------------------------------------------#

# EWSS Weekly Counts - "EWSS_data_event_counts_weekly.rds"
#------------------------------------------------------------------------------#

# "EWSS - creating data set - event counts weekly.R" was used to create this 
# data frame.

# This data set contains aggregate counts of incidents detected by 
# PPH's opioid Early Warning Surveillance System (EWSS) and consists of 
# counts of EMS CFS, ED visits, and unique EWSS events by week.

# There is one row in the data set for each day since 2019-04-01.
# Week variable lists the first day of the week.

#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::#
# Specify the location of the source script
source_script_file <- "EWSS - creating data set - event counts weekly.R"
source_script_folder <- "I:/Opioids/Data Analyses/"

# Run the source script for the data set described above.
# source(paste0(source_script_folder, source_script_file))

# EWSS Daily Counts - "EWSS_data_event_counts_daily.rds"
#------------------------------------------------------#

# "EWSS - creating data set - event counts daily.R" was used to create this 
# data frame.

# This data set contains aggregate counts of incidents detected by 
# PPH's opioid Early Warning Surveillance System (EWSS) and consists of 
# counts of EMS CFS, ED visits, and unique EWSS events by date.

# There is one row in the data set for each day since 2019-04-01.

#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::#
# > Source code (optional) ----
# Specify the location of the source script
 source_script_file <- "EWSS - creating data set - event counts daily.R"
 source_script_folder <- "I:/Opioids/Data Analyses/"

# Run the source script for the data set described above:
# source(paste0(source_script_folder, source_script_file))
 
# EWSS Event Data - "EWSS_data_events.rds"
#-----------------------------------------#

# "EWSS - creating data set - EWSS events.R" was used to create this data frame.

# This data is used for PPH's opioid Early Warning Surveillance System (EWSS)
# and consists of data on unique overdose events for which medical attention
# was sought.  The data set includes:
# a. opioid-related paramedic calls for service to Peterborough County-City 
#     Paramedics within PPH's jurisdiction (as recorded in PCCP's iMedic 
#     database)
# b. overdose-related ED visits by PPH residents to any hospital in Ontario (as
#     recorded in ACES)

# There is one row in the data set per event.

# > Data Availability
#::::::::::::::::::::#
# a. opioid-related paramedic calls for service data: 
#       is available from 2019-04-01 onwards.
# b. overdose-related ED visit data: 
#       is available from 2018-04-01 onwards.

#::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::#
# > Source code (optional) ----
# Specify the location of the source script
source_script_file <- "EWSS - creating data set - EWSS events.R"
source_script_folder <- "I:/Opioids/Data Analyses/"

# Run the source script for the data set described above:
# source(paste0(source_script_folder, source_script_file)) 

#-----------------------------------------------------------------------------#
# CONFIGURE PATHS ----
#-----------------------------------------------------------------------------#

# EWSS Data
#---------- #
# Specify the folder where the EWSS ACES file is stored
EWSS_folder <- "I:/Opioids/Data Analyses/Data/"

# Specify the name of the EWSS file with events by week
weekly_file <- "EWSS_data_event_counts_weekly.rds"

# Specify the name of the EWSS file with events by day
daily_file <- "EWSS_data_event_counts_daily.rds"

# Specify the name of the EWSS file with event data
events_file <- "EWSS_data_events.rds"


#------------------------------------------------------------------------------#
# LOAD EWSS (.rds) DATA ----
#------------------------------------------------------------------------------#

# Load the EWSS weekly .RDS file
EWSS_weekly <- readRDS(paste0(EWSS_folder, weekly_file))

# Load the EWSS daily .RDS file
EWSS_daily <- readRDS(paste0(EWSS_folder, daily_file))

# Load the EWSS events .RDS file
EWSS_events <- readRDS(paste0(EWSS_folder, events_file))


#------------------------------------------------------------------------------#
# DATA WRANGLING ----
#------------------------------------------------------------------------------#

# Create a vector with the date the last week with full data began
last_week <- max(EWSS_weekly$week[grepl("full",
                                        EWSS_weekly$data_available)])

# Create a vector with the date the week before last began
week_before_last <- last_week - weeks(1)

# Create a data frame to be used to calculate descriptive statistics of
# historical data (excludes data from the last week)
EWSS_weekly_subset <- subset(EWSS_weekly,
                             week < as.Date(last_week))

# Create a vector with the start and end dates for the 2 week period
# (covering last week and the week before last)
end_2_weeks <- last_week + days(6)
start_2_weeks <- end_2_weeks - days(13)

# Create a vector with text specifying the start/end dates for the 2 week period
text_2_weeks <- 
  paste0("(", 
         gsub(" 0", " ", format(start_2_weeks, "%B %d, %Y")), 
         " to ", 
         gsub(" 0", " ", format(end_2_weeks, "%B %d, %Y")),
         ")")

# Create a data frame to be used to summarize daily numbers of events over the 
# last two weeks
EWSS_daily_subset <- subset(EWSS_daily,
                             date <= as.Date(end_2_weeks) &
                              date >= as.Date(start_2_weeks)) %>%
  mutate(week = ifelse(date >= as.Date(week_before_last) &
                         date < as.Date(last_week),
                       "Week Before Last",
                       ifelse(date >= as.Date(last_week) &
                                date <= as.Date(end_2_weeks),
                              "Last Week",
                              NA)),
         weekday = format(date, "%A")) %>%
  dplyr::select(week, weekday, everything())


# Create a data frame to be used to summarize daily numbers of events over the 
# last two weeks
EWSS_events_subset <- subset(EWSS_events,
                             event_date <= as.Date(end_2_weeks) &
                              event_date >= as.Date(start_2_weeks))

```

<!--- NOTE: Line breaks to add space between header and report title --->
<br>

<br>


<!--- NOTE: PPH Program name --->

```{r program-name}
#| echo = FALSE

# Specify the location of the report image file
img.file <- file.path( "I:/Templates - Documents", "PPH - bars.png" )

# Specify the format of the program name text
text_format <- fp_text(bold = TRUE, 
                       font.size = 13, 
                       font.family = "Cambria", 
                       color = "#365f91")

# Print a line (paragraph) with the report image and program name
fpar_program <- fpar(
  external_img(src = img.file, height = 0.2, width = 0.61),
  ftext("Opioid EWSS", prop = text_format ),
  fp_p = fp_par(text.align = "left") )

fpar_program
```

<!--- NOTE: Document title --->

# Weekly Data Summary

<!--- NOTE: Published date --->
:::{custom-style="Publication Date"}
Published: `r gsub(" 0", " ", format(Sys.Date(), "%B %d, %Y"))`
:::

<!--- NOTE: Document body --->

```{r summary-tables}

#------------------------------------------------------------------------------#
# TABLES ----
#------------------------------------------------------------------------------#

# > Calculations: EMS CFS ----
#------------------------------------------------------------------------------#
# Retrieve the number of EMS CFS for last week
n_EMS_last_week <- 
  EWSS_weekly[EWSS_weekly$week == last_week, "EMS_count"]

# Retrieve the number of EMS CFS for the week before last
n_EMS_week_before_last <- 
  EWSS_weekly[EWSS_weekly$week == week_before_last, "EMS_count"]

# Calculate the historical average for weekly EMS CFS (excluding last week)
mean_EMS_weekly <- round(mean(EWSS_weekly_subset$EMS_count, na.rm = TRUE), 1)


# > Calculations: ED visits ----
#------------------------------------------------------------------------------#
# Retrieve the number of ED visits for last week
n_ED_last_week <- 
  EWSS_weekly[EWSS_weekly$week == last_week, "ED_count"]

# Retrieve the number of ED visits for the week before last
n_ED_week_before_last <- 
  EWSS_weekly[EWSS_weekly$week == week_before_last, "ED_count"]

# Calculate the historical average for weekly ED visits (excluding last week)
mean_ED_weekly <- round(mean(EWSS_weekly_subset$ED_count, na.rm = TRUE), 1)


# > Calculations: EWSS events ----
#------------------------------------------------------------------------------#
# Retrieve the number of EWSS events for last week
n_EWSS_last_week <- 
  EWSS_weekly[EWSS_weekly$week == last_week, "EWSS_count"]

# Retrieve the number of EWSS events for the week before last
n_EWSS_week_before_last <- 
  EWSS_weekly[EWSS_weekly$week == week_before_last, "EWSS_count"]

# Calculate the historical average for weekly EWSS events (excluding last week)
mean_EWSS_weekly <- round(mean(EWSS_weekly_subset$EWSS_count, na.rm = TRUE), 1)


# > Table Set-Up: EMS calls ----
#------------------------------------------------------------------------------#
# Create a vector with summary data on EMS CFS during the last week
EMS_last_week <- c("Last Week",
                   paste0("(",
                          gsub(" 0",
                               " ",
                               format(last_week, "%b %d")),
                          " to ",
                          gsub(" 0",
                               " ",
                               format(last_week + days(6), "%b %d")),
                          ")"),
                   n_EMS_last_week)

# Create a vector with summary data on EMS CFS during the week before last
EMS_week_before_last <- c("Week Before Last",
                          paste0("(", 
                                 gsub(" 0",
                                      " ",
                                      format(week_before_last, "%b %d")), 
                                 " to ", 
                                 gsub(" 0",
                                      " ",
                                      format(week_before_last + days(6), "%b %d")),
                                 ")"),
                          n_EMS_week_before_last)

# Create a vector with the historical average EMS CFS
EMS_historical <- c("Historical Average",
                    "EMS 911 calls per week",
                     mean_EMS_weekly)

# Create a data frame with summary information on weekly EMS CFS
EMS_weekly_summary <- data.frame(EMS_last_week,
                                 EMS_week_before_last,
                                 EMS_historical) %>%
  mutate(event_type = "EMS 911 calls") %>%
  dplyr::select(event_type, everything())

# > Table Set-Up: ED visits ----
#------------------------------------------------------------------------------#
# Create a vector with summary data on ED visits during the last week
ED_last_week <- c("Last Week",
                  paste0("(",
                         gsub(" 0",
                              " ",
                              format(last_week, "%b %d")),
                         " to ",
                         gsub(" 0",
                              " ",
                              format(last_week + days(6), "%b %d")),
                         ")"),
                  n_ED_last_week)

# Create a vector with summary data on ED visits during the week before last
ED_week_before_last <- c("Week Before Last",
                         paste0("(", 
                                gsub(" 0",
                                     " ",
                                     format(week_before_last, "%b %d")), 
                                " to ", 
                                gsub(" 0",
                                     " ",
                                     format(week_before_last + days(6), "%b %d")),
                                ")"),
                         n_ED_week_before_last)

# Create a vector with the historical average ED visits
ED_historical <- c("Historical Average",
                   "ED visits per week",
                    mean_ED_weekly)

# Create a data frame with summary information on weekly ED visits
ED_weekly_summary <- data.frame(ED_last_week,
                                ED_week_before_last,
                                ED_historical) %>%
  mutate(event_type = "ED visits") %>%
  dplyr::select(event_type, everything())

# > Table Set-Up: EWSS events ----
#------------------------------------------------------------------------------#
# Create a vector with summary data on EWSS events during the last week
EWSS_last_week <- c("Last Week",
                     paste0("(",
                            gsub(" 0",
                                 " ",
                                format(last_week, "%b %d")),
                            " to ",
                            gsub(" 0",
                                 " ",
                                 format(last_week + days(6), "%b %d")),
                            ")"),
                     n_EWSS_last_week)

# Create a vector with summary data on EWSS events during the week before last
EWSS_week_before_last <- c("Week Before Last",
                           paste0("(", 
                                  gsub(" 0",
                                       " ",
                                       format(week_before_last, "%b %d")), 
                                  " to ", 
                                  gsub(" 0",
                                       " ",
                                       format(week_before_last + days(6), "%b %d")),
                                  ")"),
                            n_EWSS_week_before_last)

# Create a vector with the historical average EWSS events
EWSS_historical <- c("Historical Average",
                     "EWSS events per week",
                      mean_EWSS_weekly)

# Create a data frame with summary information on weekly EWSS events
EWSS_weekly_summary <- data.frame(EWSS_last_week,
                                  EWSS_week_before_last,
                                  EWSS_historical) %>%
  mutate(event_type = "EWSS events") %>%
  dplyr::select(event_type, everything())

# > Summary Table: EMS calls ----
#------------------------------------------------------------------------------#
flextable(EMS_weekly_summary) %>%
  delete_part(part = "header") %>%
  border_remove() %>%
  bold(i = c(1, 3)) %>%
  fontsize(i = 2, size = 8) %>%
  fontsize(i = 3, size = 14) %>%
  merge_at(i = 1:3, j = 1) %>%
  bg(j = 1, bg = EMS_colour) %>%
  flextable::rotate(j = 1, rotation = "btlr", align = "center") %>%
  hrule(rule = "exact")  %>%
  border_outer(part="all", border = EMS_border )%>%
  valign(i = 2, valign = "top") %>%
  padding(i = 2, padding = 0) %>%
  padding(i = 1, padding.bottom = 0, padding.top = 2) %>%
  padding(j = 1, padding = 0) %>%
  align(align = "center", part = "all") %>%
  valign(i = 1, j = 2:4, valign = "bottom") %>%
  flextable::compose(i = 1, j = 1, as_paragraph(as_chunk('EMS calls'))) %>%
  color(j = 1, color = "#FFFFFF") %>%
  autofit() %>%
  width( j = 1, 0.75, unit = "in")

# > Line Break ----
#------------------------------------------------------------------------------#
# Specify the format of line break text
text_format <- fp_text(bold = TRUE, 
                       font.size = 6, 
                       font.family = "Arial", 
                       color = "#365f91")

# Print a line break (to add space between the summary tables)
fpar_br <- fpar(
  ftext("\n", prop = text_format ),
  fp_p = fp_par(text.align = "left") )

fpar_br


# > Summary Table: ED visits ----
#------------------------------------------------------------------------------#
flextable(ED_weekly_summary) %>%
  delete_part(part = "header") %>%
  border_remove() %>%
  bold(i = c(1, 3)) %>%
  fontsize(i = 2, size = 8) %>%
  fontsize(i = 3, size = 14) %>%
  merge_at(i = 1:3, j = 1) %>%
  bg(j = 1, bg = ED_colour) %>%
  flextable::rotate(j = 1, rotation = "btlr", align = "center") %>%
  hrule(rule = "exact")  %>%
  border_outer(part="all", border = ED_border )%>%
  valign(i = 2, valign = "top") %>%
  padding(i = 2, padding = 0) %>%
  padding(i = 1, padding.bottom = 0, padding.top = 2) %>%
  padding(j = 1, padding = 0) %>%
  align(align = "center", part = "all") %>%
  valign(i = 1, j = 2:4, valign = "bottom") %>%
  flextable::compose(i = 1, j = 1, as_paragraph(as_chunk('ED visits'))) %>%
  color(j = 1, color = "#FFFFFF") %>%
  autofit() %>%
  width( j = 1, 0.75, unit = "in")

# > Line Break ----
#------------------------------------------------------------------------------#
# Print a line break (to add space between the summary tables)
fpar_br


# > Summary Table: EWSS events ----
#------------------------------------------------------------------------------#
flextable(EWSS_weekly_summary) %>%
  delete_part(part = "header") %>%
  border_remove() %>%
  bold(i = c(1, 3)) %>%
  fontsize(i = 2, size = 8) %>%
  fontsize(i = 3, size = 14) %>%
  merge_at(i = 1:3, j = 1) %>%
  bg(j = 1, bg = EWSS_colour) %>%
  flextable::rotate(j = 1, rotation = "btlr", align = "center") %>%
  hrule(rule = "exact")  %>%
  border_outer(part="all", border = EWSS_border )%>%
  valign(i = 2, valign = "top") %>%
  padding(i = 2, padding = 0) %>%
  padding(i = 1, padding.bottom = 0, padding.top = 2) %>%
  padding(j = 1, padding = 0) %>%
  align(align = "center", part = "all") %>%
  valign(i = 1, j = 2:4, valign = "bottom") %>%
  flextable::compose(i = 1, j = 1, as_paragraph(as_chunk('Unique events'))) %>%
  color(j = 1, color = "#FFFFFF") %>%
  autofit() %>%
  width( j = 1, 0.75, unit = "in")
```


## Events over the last 12 months
```{r panel-graph}
#| echo = FALSE, 
#| fig.cap = paste0("Weekly number of events detected by the Opioid EWSS, week of ",
#|                   gsub(" 0", " ", format(last_week - weeks(51), "%B %d, %Y")),
#|                   " to week of ",
#|                   gsub(" 0", " ", format(last_week, "%B %d, %Y")),
#|                   "."), 
#| fig.id = "panel-plot", 
#| fig.cap.style = "Figure Caption"

#------------------------------------------------------------------------------#
# GRAPH ----
#------------------------------------------------------------------------------#
## > Panel plot: events by week ----

### >> Create a data frame to be used for the panel graph ----
panel_data <- EWSS_weekly %>% 
  pivot_longer(cols = ends_with("count"),
               names_pattern = "(.*)_count$",
               names_to = "event_type",
               values_to = "n") %>%
  subset(.,
         week <= last_week &
           week >= last_week - weeks(51)) %>%
  mutate(event_type = case_when(event_type == "ED" ~ "ED visits",
                                event_type == "EMS" ~ "EMS calls",
                                event_type == "EWSS" ~ "Unique events")) %>%
  mutate(event_type = factor(event_type,
                             levels = c("EMS calls",
                                        "ED visits",
                                        "Unique events")))


### >> Create a panel plot of the data ----
#------------------------------------------------------------------------------#
panel_plot <- 
  ggplot(data = panel_data,
         aes(x = week,
             y = n,
             fill = factor(event_type))) +
  
  geom_col() +
  
  facet_grid(event_type ~ .) +
  
  # Specify the colours for the bars
  scale_fill_manual(values = c( EMS_colour, ED_colour, EWSS_colour)) +
  
  # Specify the scale to use for the x axis
  scale_x_date(expand = c(0.005, 0.005),
               date_labels = "%b-%d",
               date_breaks = "4 weeks") +
  
  # Specify the scale to use for the y axis
  scale_y_continuous(expand = c(0.005, 0.1),
                     breaks = seq(10,
                                  round_any(max(panel_data$n) + 3,
                                            10,
                                            f = ceiling),
                                  10)) +
  expand_limits(y = c(0,
                      round_any(max(panel_data$n) + 3,
                                10,
                                f = ceiling))) +
  
  # Specify the labels for the graph
  labs(title = NULL,
       subtitle = NULL,
       x = "Week",
       y = "Number of Events") + 
  
  theme_minimal() +
  theme(plot.margin = unit(rep(0.5, 4), "cm"),
        legend.position = "none", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(face = "plain",
                                 color = "grey20"),
        axis.title = element_text(face = "plain",
                                  color = "grey20",
                                  size = rel(0.9)),
        axis.line.x = element_line(colour = "#333333", 
                                   size = 0.5,
                                   linetype = "solid"),
        axis.ticks.x = element_line(colour = "#333333"),
        strip.text = element_text(face = "bold",
                                  colour = "#FFFFFF",
                                  size = rel(0.57),
                                  vjust = 1),
        strip.background = element_rect(fill = "#000000",
                                        color = "#FFFFFF"))

### >> Change facet label colours to match bars ----
#------------------------------------------------------------------------------#

# Create a gtable with the grid graphical objects (grobs) for the panel plot
panel_plot_gtable <- ggplot_gtable(ggplot_build(panel_plot))

# Identify the grobs that define the background colour for the
# panel label rectangles
stripr <- which(grepl('strip-r', panel_plot_gtable$layout$name))

# Specify the colours to be  for the panel labels background fill
fills <- c(EMS_colour, ED_colour, EWSS_colour)

# Run a loop to replace the grobs with new panel label colours
k <- 1
for (i in stripr) {
  j <- which(grepl('rect',
                   panel_plot_gtable$grobs[[i]]$grobs[[1]]$childrenOrder))
  
  panel_plot_gtable$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  
  k <- k+1
}

### >> Draw the final plot ----
grid.draw(panel_plot_gtable)
```

## Events over the last 2 weeks
:::{custom-style="Publication Date"}
`r paste0(text_2_weeks)`
:::

```{r table-last-2-weeks}
#| echo = FALSE, 
#| tab.cap = paste0("Daily number of events detected by the Opioid EWSS."), 
#| tab.id = "daily-table"

#------------------------------------------------------------------------------#
# TABLE ----
#------------------------------------------------------------------------------#

# > Table Set-Up: Daily Events ----
#------------------------------------------------------------------------------#
daily_events_table <- 
  flextable(EWSS_daily_subset,
              col_keys = c("week",
                           "weekday",
                           "date",
                           "EMS_count_1d",
                           "ED_count_1d",
                           "EWSS_count_1d")) %>%
  # Label the columns
  set_header_labels(x = .,
                    values = list(
                    week = "",
                    weekday = "Date",
                    date = "Date",
                    EMS_count_1d = "EMS calls",
                    ED_count_1d = "ED visits",
                    EWSS_count_1d = "Unique events")) %>%
  
  # Format the date
  colformat_date(x = .,
                 j = "date",
                 fmt_date = "%b %d") %>%
  
  # Remove the default border
  border_remove() %>%
  
  # Add background colours to the header and first
  bg(part = "header", j = "EMS_count_1d", bg = EMS_colour) %>%
  bg(part = "header", j = "ED_count_1d", bg = ED_colour) %>%
  bg(part = "header", j = "EWSS_count_1d", bg = EWSS_colour) %>%
  bg(part = "header", j = 1:3, bg = "#000000") %>%
  bg(j = 1, bg = "#E9E9E9") %>%
  
  # Format the font
  color(part = "header", color = "#FFFFFF") %>%
  bold(part = "header",) %>%
  fontsize(part = "header", size = 10) %>%
  fontsize(part = "body", size = 8) %>%
  
  # Merge cells in the first column
  merge_at(i = 1:7, j = 1) %>%
  merge_at(i = 8:14, j = 1) %>%
  
  # Merge date-related cells in the header
  merge_at(j = 2:3, part = "header") %>%
  
  # Rotate the direction of the text in the first column
  flextable::rotate(j = 1, rotation = "btlr", align = "center") %>%
  
  # Set the height of 
 
  align(align = "center", part = "all") %>%
  align(j = 3, align = "left") %>%
  bg(j = 1, bg = "#E9E9E9") %>%
  
  # Add borders
  hline(i = 7, j = NULL, border = fp_border(color = "#333333", 
                                            width = 1, 
                                            style = "dotted")) %>%
  hline_bottom(j = NULL,
               part = "body",
               border = fp_border(color = "#333333", 
                                            width = 1, 
                                            style = "solid")) %>%
  
  vline(i = NULL, j = 6, part = "body", border = fp_border(color = "#E9E9E9", 
                                                 width = 3, 
                                                 style = "solid")) %>%
  
  #bg(i = 8:14, j = 1, bg = ED_colour) %>%
  autofit() %>%
  width(j = 1, 0.25, unit = "in")


daily_events_table

```

<!---BLOCK_MULTICOL_START--->
### Demographic Information
```{r plot-last-2-weeks}
#| echo = FALSE, 
#| fig.cap = paste0("Number of events by age group and sex."), 
#| fig.id = "age-sex-plot",
#| fig.width = 4,
#| fig.height = 2

#------------------------------------------------------------------------------#
# GRAPH ----
#------------------------------------------------------------------------------#

# > Data Set-Up ----
#------------------------------------------------------------------------------#
# Change the sex variable to a factor
EWSS_events_subset <- EWSS_events_subset %>%
  mutate(sex = factor(sex,
                      levels = c("female", "male", "missing")))

# Create a data frame with counts of events by age group and sex
EWSS_counts_age_sex <- EWSS_events_subset %>%
  aggregate(
    cbind(n_events = EWSS_event) ~
      sex + age_group_ODPRN,
    data = .,
    FUN = sum) %>%
  complete(., 
           age_group_ODPRN, sex,
           fill = list(n_events = 0)) %>%
  subset(.,
         sex != "missing")

# > Plot: Horizontal Bar Chart ----
#------------------------------------------------------------------------------#
plot_age_sex <- 
ggplot(data = EWSS_counts_age_sex) +
  # Specify how the columns should be drawn
  geom_col(
    aes (x = forcats::fct_rev(age_group_ODPRN),
         y = n_events,
         fill = sex),
    position = position_dodge(-0.9)) +
  
  # Make the columns horizontal
  coord_flip() +
  
  # Add a line for the axis
  geom_hline(yintercept = 0,
             size = 1) +
  
  # Specify the labels for the graph
  labs(title = NULL,
       subtitle = NULL,
       x = "Age Group",
       y = "Number of Events",
       fill = NULL) + 
  
  # Format the plot
  theme_minimal() +
  theme(panel.grid.major.x = element_line(color = "#333333",
                                          size = 0.75,
                                          linetype = 3),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(face = "plain",
                                 color = "grey20"),
        axis.title = element_text(face = "plain",
                                  color = "grey20",
                                  size = rel(1)),
        axis.title.y = element_text(angle = 0, 
                                    hjust = 0,
                                    margin = margin(t = 0,
                                                    r = -25)))
        

# Draw the plot
plot_age_sex
```
`r run_columnbreak()`

### EMS Call Details

```{r summary-last-2-weeks}
#| echo = FALSE

#------------------------------------------------------------------------------#
# SUMMARY STATISTICS ----
#------------------------------------------------------------------------------#

## > Calculations: calls in the last 2 weeks ----
#------------------------------------------------------------------------------#
# Find the total number of EMS 911 calls in the last 2 weeks
last_2_weeks_CFS_n <- sum(EWSS_events_subset$EMS_record == 1)


## > Calculations: Call locations ----
#------------------------------------------------------------------------------#

## >> Outdoors ----

# Calculate the number of calls to outdoor locations
outdoors_CFS_n <- sum(EWSS_events_subset$EMS_record == 1 &
                     EWSS_events_subset$EMS_outdoors == 1,
                   na.rm = TRUE)

# Calculate the percent of calls to outdoor locations
outdoors_CFS_pct <- scales::percent(outdoors_CFS_n / last_2_weeks_CFS_n)

# Create text to be used to describe the number of calls to outdoor locations
outdoors_text <- ifelse(outdoors_CFS_n != 1,
                        paste0(outdoors_CFS_n,
                               " calls (",
                               outdoors_CFS_pct,
                               ")"),
                        paste0(outdoors_CFS_n,
                               " call (",
                               outdoors_CFS_pct,
                               ")"))

#------------------------------------------------------------------------------#
## >> Private Residences ----

# Calculate the number of calls to private residences
residences_CFS_n <- sum(EWSS_events_subset$EMS_record == 1 &
                     EWSS_events_subset$EMS_residence == 1,
                   na.rm = TRUE)

# Calculate the percent of calls to private residences
residences_CFS_pct <- scales::percent(residences_CFS_n / last_2_weeks_CFS_n)

# Create text to be used to describe the number of calls to private residences
residences_text <- ifelse(residences_CFS_n != 1,
                          paste0(residences_CFS_n,
                                 " calls (",
                                 residences_CFS_pct,
                                 ")"),
                          paste0(residences_CFS_n,
                                 " call (",
                                 residences_CFS_pct,
                                 ")"))

#------------------------------------------------------------------------------#
## >> Other Locations ----

# Calculate the number of calls to other locations
other_location_CFS_n <- last_2_weeks_CFS_n - outdoors_CFS_n - residences_CFS_n

# Calculate the percent of calls to private residences
other_location_CFS_pct <- 
  scales::percent(other_location_CFS_n / last_2_weeks_CFS_n)

# Create text to be used to describe the number of calls to private residences
other_location_text <- ifelse(other_location_CFS_n != 1,
                              paste0(other_location_CFS_n,
                                     " calls (",
                                     other_location_CFS_pct,
                                     ")"),
                              paste0(other_location_CFS_n,
                                     " call (",
                                     other_location_CFS_pct,
                                     ")"))


## > Calculations:  Transport to Hospital ----
#------------------------------------------------------------------------------#
# Calculate the number of calls to where the client refused transport
refused_transport_CFS_n <- sum(EWSS_events_subset$EMS_record == 1 &
                                 EWSS_events_subset$EMS_refused_transport == 1,
                               na.rm = TRUE)

# Calculate the percent of calls to private residences
refused_transport_CFS_pct <- 
  scales::percent(refused_transport_CFS_n / last_2_weeks_CFS_n)

# Create text to be used to describe the number of calls where transport was
# refused
refused_transport_text <- ifelse(refused_transport_CFS_n != 1,
                                 paste0(refused_transport_CFS_n,
                                        " calls (",
                                        refused_transport_CFS_pct,
                                        ")"),
                                 paste0(refused_transport_CFS_n,
                                        " call (",
                                        refused_transport_CFS_pct,
                                        ")"))



```
:::{custom-style="Publication Date"}
 `r paste0( "(for the ", last_2_weeks_CFS_n, " calls in the last 2 weeks)")`
:::

***Location***

 * at `r paste0(outdoors_text)` the person was outdoors
 * at `r paste0(residences_text)` the person was at a private residence


<br>

***Transport to Hospital***

* at `r paste0(refused_transport_text)` the person declined to be taken to a hospital

<!---BLOCK_MULTICOL_STOP{widths: [4,3], space: 0.2, sep: false}--->
